Diverse Genotype-by-Weather Interactions in Switchgrass

### 2024-07-17 manuscript/revision2/revision2.tex
revision2: Sync cross-references between revision, SI Appendix, and response letter.
Also, add Figures to response letter and change templating to allow this

Plant phenological timings are major components of plant fitness
affected by multiple external environmental cues (e.g.~degree of winter
chilling, day length, temperature, and water availability) that signal
existing or upcoming growing conditions (1--4). Genetic responses to
environmental cues determine the speed, timing, and energy apportioned
to vegetative and reproductive growth and shape both the individual's
lifespan and its lifetime production of viable seed. Day length (or
photoperiod) is one of the most predictable environmental cues, and
genetic sensitivity to photoperiod protects plants from potentially
fatal consequences of phenological responses to temperature cues at the
``wrong'' time of year. However, the usefulness of specific
environmental cues depends on both features of the environment, such as
cue predictability and relevance, and the species' adaptive strategies
(5). Species with wide natural distributions can have multiple distinct
environmentally cued phenological responses: for example, populations of
sunflower (\emph{Helianthus annuus}) exhibit day-neutral, facultative
short day, and facultative long-day flowering responses, which vary with
their environments (6, 7). Distinct genetic responses in different
environments are known as genotype-by-environment interactions, or GxE.

Flowering time, or the transition from vegetative to reproductive
growth, is a common subject of GxE research (6--13), a key output of
selection driving adaptation to local environments (2, 14--16), and a
selection target for crop improvement to adapt crops to local or future
environments (17). Changing flowering responsiveness to photoperiod cues
has allowed geographic range expansion and increased yields in several
cereal species (18--22) and other crops (23, 24). Recent statistical
advances in studying phenological GxE have involved determining critical
environmental indices before the phenological event occurs, such as
photothermal time within a critical growth window (11). However, most
studies of flowering GxE focus on finding a single, best fitting form of
genotype-environment covariance, despite the key expectation that
different genetic subpopulations, and even different genomic regions,
have likely evolved distinct patterns of GxE (25). Additionally, despite
theoretical predictions that local adaptation should involve
antagonistic pleiotropy, or alleles with effects with opposing fitness
outcomes (26--29), previous empirical work has found limited evidence of
antagonistic pleiotropy (14, 30, 31). However, this work has been
limited by a known statistical bias that reduced detection of genetic
effects that differ in sign (30, 32, 33). Thus, despite substantial
interest in the frequencies of various forms of GxE, the frequency of
sign-changing GxE relative to other forms of GxE remains unknown.

Previous research suggests that switchgrass phenological timings should
have GxWeather and that these timings could differ by genetic
subpopulation. Switchgrass is considered a short-day plant with
reproductive development strongly linked to day of the year (34).
However, as part of its wide environmental adaptation across the eastern
half of North America, its photoperiodicity has been predicted to differ
by plant latitude of origin (35, 36). We previously found divergent
Midwest and Gulf genetic subpopulations of switchgrass with distinct
sets of environmental adaptations, in that both populations had distinct
genetic variation associated with each of two fitness proxies, biomass
and overwinter survival (37). The Midwest genetic subpopulation is
primarily composed of individuals from the well-studied upland
switchgrass ecotype (38, 39), while the Gulf subpopulation has
individuals from the well-studied lowland ecotype and the phenotypically
intermediate coastal ecotype (37).

Here, we test for GxWeather for two phenological timings by assigning
patterns of genetic effects on phenology at eight common gardens to many
patterns of weather covariance at these gardens. To do this, we
phenotype a diversity panel of hundreds of switchgrass genotypes from
the Midwest and Gulf subpopulations for the timing of vegetative and
reproductive development. We do this at eight common garden locations
spanning 17 degrees of latitude: these gardens cover the majority of the
latitudinal and climatic range of switchgrass and capture the most
comprehensive picture to date of the environmental variation this
species encounters. We define multiple ways phenological timings might
covary with weather (Table 1) and additional ways phenological timings
might vary by garden (SI Appendix, Section S1), then jointly re-estimate
genetic effects on these timings at all eight common gardens using the
set of these covariance matrices that significantly improved the modeled
log-likelihood when included (SI Appendix, Section S2-S5) (40). We use
the Bayesian framework \emph{mash} (multivariate adaptive shrinkage)
developed by (40), to refine effect size estimates from genome-wide
association (GWAS). \emph{Mash} allows us to identify and specify
multiple covariance structures among genetic effect estimates across
sites, including structures that represent covariance in weather
variables of interest. Importantly, this method circumvents statistical
biases in detecting genetic effects with the same or opposite signs
(41). To confirm our genetic mapping of GxWeather, we compare genomic
locations of the significant posterior effect estimates from \emph{mash}
to mapping results from an outbred mapping population grown at the same
sites. Our analyses allow us to describe the weather cues and types of
GxE affecting phenology in two divergent natural populations of
switchgrass across the species' latitudinal range.

@@

We expected to observe common rank-changing GxE at the level of
individual loci as this is a key theoretical prediction of local
adaptation (26--29). To determine the frequency of rank-changing GxE, we
used the local false sign rate (lfsr), an analogue of the lfdr that
establishes confidence in the effect sign, not the effect's difference
from zero, to determine significance. We required lfsr significance (p
\textless{} 0.05) in both gardens to include effects. This means that
our tests for a sign change between gardens carry an equal statistical
burden to those for effects with the same sign. We separated kinds of
effects at the level of individual loci into SNP effects that differ in
sign between gardens (effects with rank-changing GxE between gardens),
SNP effects that differ in magnitude (effects that are large in one
garden or region and smaller in others), and SNP effects that are
indistinguishable in two gardens (similarly large or small in
comparisons between gardens) (Figure~\ref{fig-effects} A).

@@

We sought additional experimental support the occurrence and location of
our significant SNP effect re-estimates using an independent pseudo-F2
mapping population created from Gulf \& Midwest individuals and grown at
the same sites (Figure~\ref{fig-qtl} A,B). We conducted quantitative
trait loci (QTL) mapping of flowering as functions of five environmental
cues that we also used as covariance matrices in \emph{mash}, and
identified eight QTL for flowering date, eight QTL for flowering as a
function of day length change two days prior, one QTL for the start of
vegetative growth, and two QTL for vegetative growth as a function of
daylength change one day prior, all of which showed QTL by environment
interactions (SI Appendix, Figure S4). All QTL for flowering overlapped
one or more homologs from rice or \emph{A. thaliana} with functionally
validated roles in flowering (SI Appendix, Dataset 7); the QTL on Chr04K
overlapped a gene recently functionally validated for flowering in
switchgrass (42). All flowering and green-up QTL intervals contained at
least one SNP significant in at least one \emph{mash} run at a
log10-transformed Bayes Factor \textgreater{} 2, or in the 1\% tail of
significance, whichever was stricter (SI Appendix, Dataset 8). We also
looked for enrichments of \emph{mash} SNPs in the 1\% tail of
significance (the `\emph{mash} 1\% tail') within each QTL interval. At
the 5\% level, three QTL had enrichments of SNPs in the \emph{mash} 1\%
tail. Overall, there were five significant enrichments (p \textless{}
0.05, hypergeometric test) of SNPs in the \emph{mash} 1\% tail in the
QTL intervals. Thus, we were able to experimentally support the genomic
windows of some re-estimates of significant SNP effects with a QTL
mapping experiment using a separate mapping population.

@@

Our analysis of the timing of vegetative and reproductive growth
revealed many alleles with rank-changing GxE, or sign changes in their
effects between the Texas and North gardens (Figure~\ref{fig-effects}
B). The Gulf \& Both subpopulations had rank-changing GxE for green-up
date, while the Midwest subpopulation had rank-changing GxE for
flowering date. As phenological timings are major components of plant
fitness, this result supports theoretical models that local adaptation
should involve antagonistic pleiotropy at the level of individual loci
(26--29). In addition, it advances local adaptation research by using
more than two field sites and a wide range of genetic variation to
determine that rank-changing GxE for phenological timings is common in
small genomic regions (14, 43, 44).

@@

In 2019, we scored two phenological events every two days in two mapping
populations of switchgrass, a diversity panel and a pseudo-F2 cross,
planted at eight common garden locations (39, 44, 45). We scored the
onset of vegetative growth, or green-up date, as the day of the year
when 50\% of the tiller area of the crown of the plant cut the previous
year had green growth. The onset of reproductive growth, or flowering
date, was the day of the year when 50\% of the plant tillers had
panicles undergoing anthesis.

The formation and resequencing of the diversity panel has been described
previously (37). The diversity panel contained 134 sequenced, clonally
propagated individuals from the Midwest genetic subpopulation, and 229
from the Gulf genetic subpopulation. To allow for the possibility that
different subpopulations had different strengths of connection between
our phenotypes and genotypes (46), we conducted three sets of genetic
analyses: on Gulf and Midwest genotypes separately, and on both
subpopulations together (`Both' subpopulations). Analyses to determine
narrow-sense heritability (h\textsuperscript{2}) for green-up and
flowering were done using linear mixed models and followed (37) (SI
Appendix, Section S6).

To confirm candidate genomic regions found using \emph{mash} on the
diversity panel, we analyzed flowering in an outbred pseudo-F2 cross
between four individuals, two Midwest and two Gulf individuals. The
formation of this mapping population has been described previously (39);
additional details on QTL mapping can be found in SI Appendix, Section
S7. To be directly comparable to the diversity panel data, only 2019
phenology data from the pseudo-F2 cross from the same eight common
garden sites were used.

@@

Using the lfsr rather than the local false discovery rate (lfdr) is a
critical change in our ability to detect alleles directly contributing
to rank-changing GxE between environments. The lfdr, like other measures
of FDR, focuses on if we have enough evidence to reject the null
hypothesis that an effect j is 0, or that there is a significant effect.
Previous studies of antagonistic pleiotropy (e.g. (44)) have used the
lfdr or equivalent statistical tests to detect antagonistic pleiotropy.
These tests were conservative, in that they required two non-zero
effects of different signs, while tests for differential sensitivity
required only one non-zero effect. This previous work recognized that
this testing bias could lead to undercounting occurrences of
antagonistic pleiotropy (30, 33), and sought to reduce it by permutation
(32). However, using the lfsr to test for allelic effects that differ in
sign does not undercount these occurences, as this statistic answers a
fundamentally different question. For each effect \(j\), the \(lfsr_j\)
is defined as the probability that we make an error in the sign of
effect \(j\) if we were forced to declare the effect positive or
negative (41). Thus, rather than asking ``Are these two effects
different?'' - as we reasonably expect two effects to be, even if this
difference cannot be measured - the local false sign rate answers a more
meaningful question: Can we be confident in the sign of this effect?

@@

\bibitem[\citeproctext]{ref-wadgymar2017identifying}
\CSLLeftMargin{14. }%
\CSLRightInline{S. M. Wadgymar, \emph{et al.}, Identifying targets and
agents of selection: Innovative methods to evaluate the processes that
contribute to local adaptation. \emph{Methods in Ecology and Evolution}
\textbf{8}, 738--749 (2017).}

\bibitem[\citeproctext]{ref-blumel2015flowering}
\CSLLeftMargin{15. }%
\CSLRightInline{M. Blümel, N. Dally, C. Jung, Flowering time regulation
in crops---what did we learn from arabidopsis? \emph{Current opinion in
biotechnology} \textbf{32}, 121--129 (2015).}

\bibitem[\citeproctext]{ref-fournier-level2016}
\CSLLeftMargin{16. }%
\CSLRightInline{A. Fournier-Level, \emph{et al.},
\href{https://doi.org/10.1073/pnas.1517456113}{Predicting the
evolutionary dynamics of seasonal adaptation to novel climates in
{\emph{Arabidopsis thaliana}}}. \emph{Proceedings of the National
Academy of Sciences} \textbf{113} (2016).}

\bibitem[\citeproctext]{ref-jung2009flowering}
\CSLLeftMargin{17. }%
\CSLRightInline{C. Jung, A. E. Müller, Flowering time control and
applications in plant breeding. \emph{Trends in plant science}
\textbf{14}, 563--573 (2009).}

\bibitem[\citeproctext]{ref-turner2005pseudo}
\CSLLeftMargin{18. }%
\CSLRightInline{A. Turner, J. Beales, S. Faure, R. P. Dunford, D. A.
Laurie, The pseudo-response regulator ppd-H1 provides adaptation to
photoperiod in barley. \emph{Science} \textbf{310}, 1031--1034 (2005).}

\bibitem[\citeproctext]{ref-faure2012mutation}
\CSLLeftMargin{19. }%
\CSLRightInline{S. Faure, \emph{et al.}, Mutation at the circadian clock
gene EARLY MATURITY 8 adapts domesticated barley (hordeum vulgare) to
short growing seasons. \emph{Proceedings of the National Academy of
Sciences} \textbf{109}, 8328--8333 (2012).}

\bibitem[\citeproctext]{ref-hung2012zmcct}
\CSLLeftMargin{20. }%
\CSLRightInline{H.-Y. Hung, \emph{et al.}, ZmCCT and the genetic basis
of day-length adaptation underlying the postdomestication spread of
maize. \emph{Proceedings of the National Academy of Sciences}
\textbf{109}, E1913--E1921 (2012).}

\bibitem[\citeproctext]{ref-zakhrabekova2012induced}
\CSLLeftMargin{21. }%
\CSLRightInline{S. Zakhrabekova, \emph{et al.}, Induced mutations in
circadian clock regulator mat-a facilitated short-season adaptation and
range extension in cultivated barley. \emph{Proceedings of the National
Academy of Sciences} \textbf{109}, 4326--4331 (2012).}

\bibitem[\citeproctext]{ref-yang2013oself3}
\CSLLeftMargin{22. }%
\CSLRightInline{Y. Yang, Q. Peng, G.-X. Chen, X.-H. Li, C.-Y. Wu, OsELF3
is involved in circadian clock regulation for promoting flowering under
long-day conditions in rice. \emph{Molecular Plant} \textbf{6}, 202--215
(2013).}

\bibitem[\citeproctext]{ref-pin2012multifaceted}
\CSLLeftMargin{23. }%
\CSLRightInline{P. Pin, O. Nilsson, The multifaceted roles of FLOWERING
LOCUS t in plant development. \emph{Plant, cell \& environment}
\textbf{35}, 1742--1755 (2012).}

\bibitem[\citeproctext]{ref-weller2019parallel}
\CSLLeftMargin{24. }%
\CSLRightInline{J. L. Weller, \emph{et al.}, Parallel origins of
photoperiod adaptation following dual domestications of common bean.
\emph{Journal of Experimental Botany} \textbf{70}, 1209--1219 (2019).}

\bibitem[\citeproctext]{ref-Weine2023.06.21.545998}
\CSLLeftMargin{25. }%
\CSLRightInline{E. Weine, S. P. Smith, R. K. Knowlton, A. Harpak,
Tradeoffs in modeling context dependency in complex trait genetics.
\emph{bioRxiv} (2024)
https:/doi.org/\href{https://doi.org/10.1101/2023.06.21.545998}{10.1101/2023.06.21.545998}.}

\bibitem[\citeproctext]{ref-levene1953genetic}
\CSLLeftMargin{26. }%
\CSLRightInline{H. Levene, Genetic equilibrium when more than one
ecological niche is available. \emph{The American Naturalist}
\textbf{87}, 331--333 (1953).}

\bibitem[\citeproctext]{ref-felsenstein1976theoretical}
\CSLLeftMargin{27. }%
\CSLRightInline{J. Felsenstein, The theoretical population genetics of
variable selection and migration. \emph{Annual review of genetics}
\textbf{10}, 253--280 (1976).}

\bibitem[\citeproctext]{ref-kawecki2004conceptual}
\CSLLeftMargin{28. }%
\CSLRightInline{T. J. Kawecki, D. Ebert, Conceptual issues in local
adaptation. \emph{Ecology letters} \textbf{7}, 1225--1241 (2004).}

\bibitem[\citeproctext]{ref-hedrick1986genetic}
\CSLLeftMargin{29. }%
\CSLRightInline{P. W. Hedrick, Genetic polymorphism in heterogeneous
environments: A decade later. \emph{Annual review of ecology and
systematics} \textbf{17}, 535--566 (1986).}

\bibitem[\citeproctext]{ref-des2013genotype}
\CSLLeftMargin{30. }%
\CSLRightInline{D. L. Des Marais, K. M. Hernandez, T. E. Juenger,
Genotype-by-environment interaction and plasticity: Exploring genomic
responses of plants to the abiotic environment. \emph{Annual Review of
Ecology, Evolution, and Systematics} \textbf{44}, 5--29 (2013).}

\bibitem[\citeproctext]{ref-millet2016}
\CSLLeftMargin{31. }%
\CSLRightInline{E. Millet, \emph{et al.},
\href{https://doi.org/10.1104/pp.16.00621}{Genome-wide analysis of yield
in Europe: allelic effects as functions of drought and heat scenarios}.
\emph{Plant Physiology}, pp.00621.2016 (2016).}

\bibitem[\citeproctext]{ref-anderson2013genetic}
\CSLLeftMargin{32. }%
\CSLRightInline{J. T. Anderson, C.-R. Lee, C. A. Rushworth, R. I.
Colautti, T. Mitchell-Olds, Genetic trade-offs and conditional
neutrality contribute to local adaptation. \emph{Molecular ecology}
\textbf{22}, 699--708 (2013).}

\bibitem[\citeproctext]{ref-anderson2011evolutionary}
\CSLLeftMargin{33. }%
\CSLRightInline{J. T. Anderson, J. H. Willis, T. Mitchell-Olds,
Evolutionary genetics of plant adaptation. \emph{Trends in Genetics}
\textbf{27}, 258--266 (2011).}

\bibitem[\citeproctext]{ref-mitchell1997predicting}
\CSLLeftMargin{34. }%
\CSLRightInline{R. B. Mitchell, K. J. Moore, L. E. Moser, J. O. Fritz,
D. D. Redfearn, Predicting developmental morphology in switchgrass and
big bluestem. \emph{Agronomy Journal} \textbf{89}, 827--832 (1997).}

\bibitem[\citeproctext]{ref-parrish2005biology}
\CSLLeftMargin{35. }%
\CSLRightInline{D. J. Parrish, J. H. Fike, The biology and agronomy of
switchgrass for biofuels. \emph{BPTS} \textbf{24}, 423--459 (2005).}

>>>>

Plant phenological timings are major components of plant fitness
affected by multiple external environmental cues (e.g.~degree of winter
chilling, day length, temperature, and water availability) that signal
existing or upcoming growing conditions (1--4). Genetic responses to
environmental cues determine the speed, timing, and energy apportioned
to vegetative and reproductive growth and shape the individual's
physiological responses, lifespan, and lifetime production of viable
seed. Day length (or photoperiod) is one of the most predictable
environmental cues, and genetic sensitivity to photoperiod protects
plants from potentially fatal consequences of phenological responses to
temperature cues at the ``wrong'' time of year. However, the usefulness
of specific environmental cues depends on both features of the
environment, such as cue predictability and relevance, and the species'
adaptive strategies (5). Species with wide natural distributions can
have multiple distinct environmentally cued phenological responses: for
example, populations of sunflower (\emph{Helianthus annuus}) exhibit
day-neutral, facultative short day, and facultative long-day flowering
responses, which vary with their environments (6, 7). Distinct genetic
responses in different environments are known as genotype-by-environment
interactions, or GxE.

Flowering time, or the transition from vegetative to reproductive
growth, is a common subject of GxE research (6--13), a key output of
selection driving adaptation to local environments (2, 14--17), and a
selection target for crop improvement to adapt crops to local or future
environments (18). Changing flowering responsiveness to photoperiod cues
has allowed geographic range expansion and increased yields in several
cereal species (14, 19--23) and other crops (24, 25). Recent statistical
advances in studying phenological GxE have involved determining critical
environmental indices before the phenological event occurs, such as
photothermal time within a critical growth window (11). However, most
studies of flowering GxE focus on finding a single, best fitting form of
genotype-environment covariance, despite the key expectation that
different genetic subpopulations, and even different genomic regions,
have likely evolved distinct patterns of GxE (26). Additionally, despite
theoretical predictions that local adaptation should involve
antagonistic pleiotropy, or alleles with effects with opposing fitness
outcomes (27--30), previous empirical work has found limited evidence of
antagonistic pleiotropy (15, 31, 32). However, this work has been
limited by a known statistical bias that reduced detection of genetic
effects that differ in sign (31, 33, 34). Thus, despite substantial
interest in the frequencies of various forms of GxE, the frequency of
sign-changing GxE relative to other forms of GxE remains unknown.

Previous research suggests that switchgrass phenological timings should
have GxWeather and that these timings could differ by genetic
subpopulation. Switchgrass is considered a short-day plant with
reproductive development strongly linked to day of the year (35).
However, as part of its wide environmental adaptation across the eastern
half of North America, its photoperiodicity has been predicted to differ
by plant latitude of origin (36, 37). We previously found divergent
Midwest and Gulf genetic subpopulations of switchgrass with distinct
sets of environmental adaptations, in that both populations had distinct
genetic variation associated with each of two fitness proxies, biomass
and overwinter survival (38). The Midwest genetic subpopulation is
primarily composed of individuals from the well-studied upland
switchgrass ecotype (39, 40), while the Gulf subpopulation has
individuals from the well-studied lowland ecotype and the phenotypically
intermediate coastal ecotype (38).

Here, we test for GxWeather for two phenological timings by assigning
patterns of genetic effects on phenology at eight common gardens to many
patterns of weather covariance at these gardens. To do this, we
phenotype a diversity panel of hundreds of switchgrass genotypes from
the Midwest and Gulf subpopulations for the timing of vegetative and
reproductive development. We do this at eight common garden locations
spanning 17 degrees of latitude: these gardens cover the majority of the
latitudinal and climatic range of switchgrass and capture the most
comprehensive picture to date of the environmental variation this
species encounters. We define multiple ways phenological timings might
covary with weather (Table 1) and additional ways phenological timings
might vary by garden (SI Appendix, Section S1), then jointly re-estimate
genetic effects on these timings at all eight common gardens using the
set of these covariance matrices that significantly improved the modeled
log-likelihood when included (SI Appendix, Section S2-S5) (41). We use
the Bayesian framework \emph{mash} (multivariate adaptive shrinkage)
developed by (41), to refine effect size estimates from genome-wide
association (GWAS). \emph{Mash} allows us to identify and specify
multiple covariance structures among genetic effect estimates across
sites, including structures that represent covariance in weather
variables of interest. Importantly, this method circumvents statistical
biases in detecting genetic effects with the same or opposite signs
(42). To confirm our genetic mapping of GxWeather, we compare genomic
locations of the significant posterior effect estimates from \emph{mash}
to mapping results from an outbred mapping population grown at the same
sites. Our analyses allow us to describe the weather cues and types of
GxE affecting phenology in two divergent natural populations of
switchgrass across the species' latitudinal range.

@@

We expected to observe common rank-changing GxE at the level of
individual loci as this is a key theoretical prediction of local
adaptation (27--30). To determine the frequency of rank-changing GxE, we
used the local false sign rate (lfsr), an analogue of the local false
discovery rate that establishes confidence in the effect sign, not the
effect's difference from zero, to determine significance. We required
lfsr significance (p \textless{} 0.05) in both gardens to include
effects. This means that our tests for a sign change between gardens
carry an equal statistical burden to those for effects with the same
sign. We separated kinds of effects at the level of individual loci into
SNP effects that differ in sign between gardens (effects with
rank-changing GxE between gardens), SNP effects that differ in magnitude
(effects that are large in one garden or region and smaller in others),
and SNP effects that are indistinguishable in two gardens (similarly
large or small in comparisons between gardens) (Figure~\ref{fig-effects}
A).

@@

We sought additional experimental support the occurrence and location of
our significant SNP effect re-estimates using an independent pseudo-F2
mapping population created from Gulf \& Midwest individuals and grown at
the same sites (Figure~\ref{fig-qtl} A,B). We conducted quantitative
trait loci (QTL) mapping of flowering as functions of five environmental
cues that we also used as covariance matrices in \emph{mash}, and
identified eight QTL for flowering date, eight QTL for flowering as a
function of day length change two days prior, one QTL for the start of
vegetative growth, and two QTL for vegetative growth as a function of
daylength change one day prior, all of which showed QTL by environment
interactions (SI Appendix, Figure S4). All QTL for flowering overlapped
one or more homologs from rice or \emph{A. thaliana} with functionally
validated roles in flowering (SI Appendix, Dataset 7); the QTL on Chr04K
overlapped a gene recently functionally validated for flowering in
switchgrass (43). All flowering and green-up QTL intervals contained at
least one SNP significant in at least one \emph{mash} run at a
log10-transformed Bayes Factor \textgreater{} 2, or in the 1\% tail of
significance, whichever was stricter (SI Appendix, Dataset 8). We also
looked for enrichments of \emph{mash} SNPs in the 1\% tail of
significance (the `\emph{mash} 1\% tail') within each QTL interval. At
the 5\% level, three QTL had enrichments of SNPs in the \emph{mash} 1\%
tail. Overall, there were five significant enrichments (p \textless{}
0.05, hypergeometric test) of SNPs in the \emph{mash} 1\% tail in the
QTL intervals. Thus, we were able to experimentally support the genomic
windows of some re-estimates of significant SNP effects with a QTL
mapping experiment using a separate mapping population.

@@

Our analysis of the timing of vegetative and reproductive growth
revealed many alleles with rank-changing GxE, or sign changes in their
effects between the Texas and North gardens (Figure~\ref{fig-effects}
B). The Gulf \& Both subpopulations had rank-changing GxE for green-up
date, while the Midwest subpopulation had rank-changing GxE for
flowering date. As phenological timings are major components of plant
fitness, this result supports theoretical models that local adaptation
should involve antagonistic pleiotropy at the level of individual loci
(27--30). In addition, it advances local adaptation research by using
more than two field sites and a wide range of genetic variation to
determine that rank-changing GxE for phenological timings is common in
small genomic regions (15, 44, 45).

@@

In 2019, we scored two phenological events every two days in two mapping
populations of switchgrass, a diversity panel and a pseudo-F2 cross,
planted at eight common garden locations (38, 40, 45). We scored the
onset of vegetative growth, or green-up date, as the day of the year
when 50\% of the tiller area of the crown of the plant cut the previous
year had green growth. The onset of reproductive growth, or flowering
date, was the day of the year when 50\% of the plant tillers had
panicles undergoing anthesis.

The formation and resequencing of the diversity panel has been described
previously (38). The diversity panel contained 134 sequenced, clonally
propagated individuals from the Midwest genetic subpopulation, and 229
from the Gulf genetic subpopulation. To allow for the possibility that
different subpopulations had different strengths of connection between
our phenotypes and genotypes (46), we conducted three sets of genetic
analyses: on Gulf and Midwest genotypes separately, and on both
subpopulations together (`Both' subpopulations). Analyses to determine
narrow-sense heritability (h\textsuperscript{2}) for green-up and
flowering were done using linear mixed models and followed (38) (SI
Appendix, Section S6).

To confirm candidate genomic regions found using \emph{mash} on the
diversity panel, we analyzed flowering in an outbred pseudo-F2 cross
between four individuals, two Midwest and two Gulf individuals. The
formation of this mapping population has been described previously (40);
additional details on QTL mapping can be found in SI Appendix, Section
S7. To be directly comparable to the diversity panel data, only 2019
phenology data from the pseudo-F2 cross from the same eight common
garden sites were used.

@@

Using the lfsr rather than the local false discovery rate (local FDR) is
a critical change in our ability to detect alleles directly contributing
to rank-changing GxE between environments. The local FDR, like other
measures of FDR, focuses on if we have enough evidence to reject the
null hypothesis that an effect j is 0, or that there is a significant
effect. Previous studies of antagonistic pleiotropy (e.g. (45)) have
used the local FDR or equivalent statistical tests to detect
antagonistic pleiotropy. These tests were conservative, in that they
required two non-zero effects of different signs, while tests for
differential sensitivity required only one non-zero effect. This
previous work recognized that this testing bias could lead to
undercounting occurrences of antagonistic pleiotropy (31, 34), and
sought to reduce it by permutation (33). However, using the lfsr to test
for allelic effects that differ in sign does not undercount these
occurences, as this statistic answers a fundamentally different
question. For each effect \(j\), the \(lfsr_j\) is defined as the
probability that we make an error in the sign of effect \(j\) if we were
forced to declare the effect positive or negative (42). Thus, rather
than asking ``Are these two effects different?'' - as we reasonably
expect two effects to be, even if this difference cannot be measured -
the local false sign rate answers a more meaningful question: Can we be
confident in the sign of this effect?

@@

\bibitem[\citeproctext]{ref-unterseer2016}
\CSLLeftMargin{14. }%
\CSLRightInline{S. Unterseer, \emph{et al.},
\href{https://doi.org/10.1186/s13059-016-1009-x}{A comprehensive study
of the genomic differentiation between temperate Dent and Flint maize}.
\emph{Genome Biology} \textbf{17} (2016).}

\bibitem[\citeproctext]{ref-wadgymar2017identifying}
\CSLLeftMargin{15. }%
\CSLRightInline{S. M. Wadgymar, \emph{et al.}, Identifying targets and
agents of selection: Innovative methods to evaluate the processes that
contribute to local adaptation. \emph{Methods in Ecology and Evolution}
\textbf{8}, 738--749 (2017).}

\bibitem[\citeproctext]{ref-blumel2015flowering}
\CSLLeftMargin{16. }%
\CSLRightInline{M. Blümel, N. Dally, C. Jung, Flowering time regulation
in crops---what did we learn from arabidopsis? \emph{Current opinion in
biotechnology} \textbf{32}, 121--129 (2015).}

\bibitem[\citeproctext]{ref-fournier-level2016}
\CSLLeftMargin{17. }%
\CSLRightInline{A. Fournier-Level, \emph{et al.},
\href{https://doi.org/10.1073/pnas.1517456113}{Predicting the
evolutionary dynamics of seasonal adaptation to novel climates in
{\emph{Arabidopsis thaliana}}}. \emph{Proceedings of the National
Academy of Sciences} \textbf{113} (2016).}

\bibitem[\citeproctext]{ref-jung2009flowering}
\CSLLeftMargin{18. }%
\CSLRightInline{C. Jung, A. E. Müller, Flowering time control and
applications in plant breeding. \emph{Trends in plant science}
\textbf{14}, 563--573 (2009).}

\bibitem[\citeproctext]{ref-turner2005pseudo}
\CSLLeftMargin{19. }%
\CSLRightInline{A. Turner, J. Beales, S. Faure, R. P. Dunford, D. A.
Laurie, The pseudo-response regulator ppd-H1 provides adaptation to
photoperiod in barley. \emph{Science} \textbf{310}, 1031--1034 (2005).}

\bibitem[\citeproctext]{ref-faure2012mutation}
\CSLLeftMargin{20. }%
\CSLRightInline{S. Faure, \emph{et al.}, Mutation at the circadian clock
gene EARLY MATURITY 8 adapts domesticated barley (hordeum vulgare) to
short growing seasons. \emph{Proceedings of the National Academy of
Sciences} \textbf{109}, 8328--8333 (2012).}

\bibitem[\citeproctext]{ref-hung2012zmcct}
\CSLLeftMargin{21. }%
\CSLRightInline{H.-Y. Hung, \emph{et al.}, ZmCCT and the genetic basis
of day-length adaptation underlying the postdomestication spread of
maize. \emph{Proceedings of the National Academy of Sciences}
\textbf{109}, E1913--E1921 (2012).}

\bibitem[\citeproctext]{ref-zakhrabekova2012induced}
\CSLLeftMargin{22. }%
\CSLRightInline{S. Zakhrabekova, \emph{et al.}, Induced mutations in
circadian clock regulator mat-a facilitated short-season adaptation and
range extension in cultivated barley. \emph{Proceedings of the National
Academy of Sciences} \textbf{109}, 4326--4331 (2012).}

\bibitem[\citeproctext]{ref-yang2013oself3}
\CSLLeftMargin{23. }%
\CSLRightInline{Y. Yang, Q. Peng, G.-X. Chen, X.-H. Li, C.-Y. Wu, OsELF3
is involved in circadian clock regulation for promoting flowering under
long-day conditions in rice. \emph{Molecular Plant} \textbf{6}, 202--215
(2013).}

\bibitem[\citeproctext]{ref-pin2012multifaceted}
\CSLLeftMargin{24. }%
\CSLRightInline{P. Pin, O. Nilsson, The multifaceted roles of FLOWERING
LOCUS t in plant development. \emph{Plant, cell \& environment}
\textbf{35}, 1742--1755 (2012).}

\bibitem[\citeproctext]{ref-weller2019parallel}
\CSLLeftMargin{25. }%
\CSLRightInline{J. L. Weller, \emph{et al.}, Parallel origins of
photoperiod adaptation following dual domestications of common bean.
\emph{Journal of Experimental Botany} \textbf{70}, 1209--1219 (2019).}

\bibitem[\citeproctext]{ref-Weine2023.06.21.545998}
\CSLLeftMargin{26. }%
\CSLRightInline{E. Weine, S. P. Smith, R. K. Knowlton, A. Harpak,
Tradeoffs in modeling context dependency in complex trait genetics.
\emph{bioRxiv} (2024)
https:/doi.org/\href{https://doi.org/10.1101/2023.06.21.545998}{10.1101/2023.06.21.545998}.}

\bibitem[\citeproctext]{ref-levene1953genetic}
\CSLLeftMargin{27. }%
\CSLRightInline{H. Levene, Genetic equilibrium when more than one
ecological niche is available. \emph{The American Naturalist}
\textbf{87}, 331--333 (1953).}

\bibitem[\citeproctext]{ref-felsenstein1976theoretical}
\CSLLeftMargin{28. }%
\CSLRightInline{J. Felsenstein, The theoretical population genetics of
variable selection and migration. \emph{Annual review of genetics}
\textbf{10}, 253--280 (1976).}

\bibitem[\citeproctext]{ref-kawecki2004conceptual}
\CSLLeftMargin{29. }%
\CSLRightInline{T. J. Kawecki, D. Ebert, Conceptual issues in local
adaptation. \emph{Ecology letters} \textbf{7}, 1225--1241 (2004).}

\bibitem[\citeproctext]{ref-hedrick1986genetic}
\CSLLeftMargin{30. }%
\CSLRightInline{P. W. Hedrick, Genetic polymorphism in heterogeneous
environments: A decade later. \emph{Annual review of ecology and
systematics} \textbf{17}, 535--566 (1986).}

\bibitem[\citeproctext]{ref-des2013genotype}
\CSLLeftMargin{31. }%
\CSLRightInline{D. L. Des Marais, K. M. Hernandez, T. E. Juenger,
Genotype-by-environment interaction and plasticity: Exploring genomic
responses of plants to the abiotic environment. \emph{Annual Review of
Ecology, Evolution, and Systematics} \textbf{44}, 5--29 (2013).}

\bibitem[\citeproctext]{ref-millet2016}
\CSLLeftMargin{32. }%
\CSLRightInline{E. Millet, \emph{et al.},
\href{https://doi.org/10.1104/pp.16.00621}{Genome-wide analysis of yield
in Europe: allelic effects as functions of drought and heat scenarios}.
\emph{Plant Physiology}, pp.00621.2016 (2016).}

\bibitem[\citeproctext]{ref-anderson2013genetic}
\CSLLeftMargin{33. }%
\CSLRightInline{J. T. Anderson, C.-R. Lee, C. A. Rushworth, R. I.
Colautti, T. Mitchell-Olds, Genetic trade-offs and conditional
neutrality contribute to local adaptation. \emph{Molecular ecology}
\textbf{22}, 699--708 (2013).}

\bibitem[\citeproctext]{ref-anderson2011evolutionary}
\CSLLeftMargin{34. }%
\CSLRightInline{J. T. Anderson, J. H. Willis, T. Mitchell-Olds,
Evolutionary genetics of plant adaptation. \emph{Trends in Genetics}
\textbf{27}, 258--266 (2011).}

\bibitem[\citeproctext]{ref-mitchell1997predicting}
\CSLLeftMargin{35. }%
\CSLRightInline{R. B. Mitchell, K. J. Moore, L. E. Moser, J. O. Fritz,
D. D. Redfearn, Predicting developmental morphology in switchgrass and
big bluestem. \emph{Agronomy Journal} \textbf{89}, 827--832 (1997).}

\bibitem[\citeproctext]{ref-parrish2005biology}
\CSLLeftMargin{36. }%
\CSLRightInline{D. J. Parrish, J. H. Fike, The biology and agronomy of
switchgrass for biofuels. \emph{BPTS} \textbf{24}, 423--459 (2005).}
